Value-Ordering, Discrepancies, and Restarts in Subgraph Solvers: \\ Some Half-Baked Mucking Around

### 2017-09-25 paper/paper.tex
Small skip to fit
Notational consistency
I like green boxes
Plotting

\documentclass{article}
\usepackage{ijcai17}
\usepackage{times}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{tikz}

\usepackage{showframe}

@@

\newcommand{\siplabel}[1]{\label{line:sip:#1}}
\begin{algorithm}[p]\DontPrintSemicolon\small
    \begin{tikzpicture}[remember picture,overlay]
        \coordinate (restart1sc) at ($(pic cs:restart1s) + (0, 0.15)$);
        \coordinate (restart1ec) at ($(pic cs:restart1e) + (0, 0.00)$);
        \node [fill=chromaygb3, rounded corners, fit=(restart1sc) (restart1ec)] { };
        \coordinate (restart2sc) at ($(pic cs:restart2s) + (0, 0.15)$);
        \coordinate (restart2ec) at ($(pic cs:restart2e) + (0, 0.00)$);
        \node [fill=chromaygb3, rounded corners, fit=(restart2sc) (restart2ec)] { };
        \coordinate (restart3sc) at ($(pic cs:restart3s) + (0, 0.15)$);
        \coordinate (restart3ec) at ($(pic cs:restart3e) + (0, 0.00)$);
        \node [fill=chromaygb3, rounded corners, fit=(restart3sc) (restart3ec)] { };
        \coordinate (restart4sc) at ($(pic cs:restart4s) + (0, 0.15)$);
        \coordinate (restart4ec) at ($(pic cs:restart4e) + (0, 0.00)$);
        \node [fill=chromaygb3, rounded corners, fit=(restart4sc) (restart4ec)] { };
        \coordinate (restart5sc) at ($(pic cs:restart5s) + (0, 0.15)$);
        \coordinate (restart5ec) at ($(pic cs:restart5e) - (0, 0.10)$);
        \coordinate (restart5rc) at ($(pic cs:restart5r) + (0, 0.00)$);
        \node [fill=chromaygb3, rounded corners, fit=(restart5sc) (restart5ec) (restart5rc)] { };
        \coordinate (restart6sc) at ($(pic cs:restart6s) + (0, 0.15)$);
        \coordinate (restart6ec) at ($(pic cs:restart6e) + (0, 0.00)$);
        \node [fill=chromaygb3, rounded corners, fit=(restart6sc) (restart6ec)] { };
    \end{tikzpicture}

@@

\medskip

@@

    \KwSty{or} \KwSty{restart} \;

@@

                \nl Post nogoods $\{B \wedge (v \mapsto c) \rightarrow \bot : c \in C \}$\tikzmark{restart5r}\;

@@

        \nl Trigger nogoods containing $(v \mapsto v')$ \;

@@

\begin{description}
    \item[Tailored] Where we select vertices from highest degree to lowest degree (which is done by
        permuting the graph at the top of search).
    \item[Anti-Tailored] Where we select vertices from lowest degree to highest degree.
    \item[Extra Tiebreaking] Where we select vertices from highest degree to lowest degree,
        tiebreaking on highest sum of neighbour degrees.
    \item[Random] Where we select a branching vertex at random by (dynamically, that is, we shuffle
        the vertices before entering the for loop, rather than by randomly permuting the graph once at the
        top of search).
    \item[Tailor-Weighted Random] Where we shuffle the vertices before each for loop, but instead of
        picking a vertex uniformly at random, we use a weight of
        $2^{\left|\neighbourhood(v)\right|}$ when deciding whether to branch on vertex $v$
        next.\footnote{Actually, we cheat a bit to avoid range issues with random number generation:
        we give the vertex with highest degree in the entire graph weight $2^{50}$, and then give
        lower degree vertices smaller powers, giving every vertex weight at least 1. This is a bit
        of hack but getting it perfectly right is hard.} This scheme heavily prefer vertices of high
        degree, but will give the same chance of being selected next to two vertices of equal
        degree. This also introduces an element of randomness, which will be important for restarts.
\end{description}

@@

?? Non-induced, compare to Glasgow, LAD, PathLAD, SND?, VF2

?? Induced, compare to Glasgow, LAD, PathLAD, VF2, VF3, McSplit.

@@

?? DDS counting bias both ways, LDS

@@

?? Random, tailored, antitailored, random with restarts, tailored biased, tailored biased with
restarts. Satisfiable and unsatisfiable split.

?? Breakdown by family

\subsection{Near the Phase Transition}

?? Closer look at SAT instances near the phase transition

>>>>

\documentclass{article}
\usepackage{ijcai17}
\usepackage{times}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{tikz}
\usepackage{cleveref}

% \usepackage{showframe}

@@

\newcommand{\siplabel}[1]{\label{line:sip:#1}}
\begin{algorithm}[p]\DontPrintSemicolon\small
    \begin{tikzpicture}[remember picture,overlay]
        \coordinate (restart1sc) at ($(pic cs:restart1s) + (0, 0.15)$);
        \coordinate (restart1ec) at ($(pic cs:restart1e) + (0, 0.00)$);
        \node [fill=chromaygb3, rounded corners, fit=(restart1sc) (restart1ec)] { };
        \coordinate (restart2sc) at ($(pic cs:restart2s) + (0, 0.15)$);
        \coordinate (restart2ec) at ($(pic cs:restart2e) + (0, 0.00)$);
        \node [fill=chromaygb3, rounded corners, fit=(restart2sc) (restart2ec)] { };
        \coordinate (restart3sc) at ($(pic cs:restart3s) + (0, 0.15)$);
        \coordinate (restart3ec) at ($(pic cs:restart3e) + (0, 0.00)$);
        \node [fill=chromaygb3, rounded corners, fit=(restart3sc) (restart3ec)] { };
        \coordinate (restart4sc) at ($(pic cs:restart4s) + (0, 0.15)$);
        \coordinate (restart4ec) at ($(pic cs:restart4e) + (0, 0.00)$);
        \node [fill=chromaygb3, rounded corners, fit=(restart4sc) (restart4ec)] { };
        \coordinate (restart5sc) at ($(pic cs:restart5s) + (0, 0.15)$);
        \coordinate (restart5ec) at ($(pic cs:restart5e) - (0, 0.10)$);
        \coordinate (restart5rc) at ($(pic cs:restart5r) + (0, 0.00)$);
        \node [fill=chromaygb3, rounded corners, fit=(restart5sc) (restart5ec) (restart5rc)] { };
        \coordinate (restart6sc) at ($(pic cs:restart6s) + (0, 0.15)$);
        \coordinate (restart6ec) at ($(pic cs:restart6e) + (0, 0.00)$);
        \node [fill=chromaygb3, rounded corners, fit=(restart6sc) (restart6ec)] { };
        \coordinate (restart7sc) at ($(pic cs:restart7s) + (0, 0.15)$);
        \coordinate (restart7ec) at ($(pic cs:restart7e) + (0, 0.00)$);
        \node [fill=chromaygb3, rounded corners, fit=(restart7sc) (restart7ec)] { };
        \coordinate (restart8sc) at ($(pic cs:restart8s) + (0.05, 0.15)$);
        \coordinate (restart8ec) at ($(pic cs:restart8e) + (0, 0.00)$);
        \node [fill=chromaygb3, rounded corners, fit=(restart8sc) (restart8ec)] { };
    \end{tikzpicture}

@@

\smallskip

@@

    \tikzmark{restart8s}\KwSty{or} \KwSty{restart}\tikzmark{restart8e} \;

@@

                \nl Post nogoods $\{B \wedge (v \mapsto c) \Rightarrow \bot : c \in C \}$\tikzmark{restart5r}\;

@@

        \nl \tikzmark{restart7s}Trigger nogoods containing $(v \mapsto v')$\tikzmark{restart7e} \;

@@

\begin{description}
    \item[Tailored] Where we select vertices from highest degree to lowest degree (which is done by
        permuting the graph at the top of search).
    \item[Anti] Where we select vertices from lowest degree to highest degree.
    \item[Tiebreaking] Where we select vertices from highest degree to lowest degree,
        tiebreaking on highest sum of neighbour degrees.
    \item[Random] Where we select a branching vertex at random by (dynamically, that is, we shuffle
        the vertices before entering the for loop, rather than by randomly permuting the graph once at the
        top of search).
    \item[Weighted] Where we shuffle the vertices before each for loop, but instead of
        picking a vertex uniformly at random, we use a weight of
        $2^{\left|\neighbourhood(v)\right|}$ when deciding whether to branch on vertex $v$
        next.\footnote{Actually, we cheat a bit to avoid range issues with random number generation:
        we give the vertex with highest degree in the entire graph weight $2^{50}$, and then give
        lower degree vertices smaller powers, giving every vertex weight at least 1. This is a bit
        of hack but getting it perfectly right is hard.} This scheme heavily prefer vertices of high
        degree, but will give the same chance of being selected next to two vertices of equal
        degree. This also introduces an element of randomness, which will be important for restarts.
\end{description}

@@

?? Non-induced, compare to Glasgow, LAD, PathLAD, SND?, VF2, using tailored

?? Possibly also do induced, compare to Glasgow, LAD, PathLAD, VF2, VF3, McSplit.

\subsection{Value Ordering Heuristics}

?? \cref{figure:value-ordering-heuristics}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-value-ordering-heuristics.pdf}

    \caption{Cumulative number of instances solved over time, using the five different
    value-ordering heuristics. The top three lines are very close together, with the weighted
    heuristic being worse for low runtimes and slightly better towards the end.}
    \label{figure:value-ordering-heuristics}
\end{figure}

@@

?? Results for DDS counting discrepancies both ways, maybe LDS too. Also look just at satisfiable
instances.

@@

\begin{figure}
    \centering
    \includegraphics*{gen-graph-restarts.pdf}

    \caption{Cumulative number of instances solved over time, with and without restarts.}
    \label{figure:restarts}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-scatter.pdf}

    \caption{Instance by instance comparison of the basic algorithm with the tailored heuristic,
    versus weighted with restarts.}
    \label{figure:restarts}
\end{figure}

?? \cref{figure:restarts}

?? breakdown by family
